MINOS Handover Plots

### 2024-03-06 minos/validation/handovers.Rmd
Tweaks to data in and qaly visualisation functions. Added a script for checking pathway response to intervention

# sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
# spaghetti_plot(sf12.m.spag.sample, 'SF_12_MCS',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(sf12.m.spag.sample, 'SF_12_MCS',
#                save = shall.we.save,
#                save.path = save.path)

>>>>

#sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.m.spag, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
